Radio Sources in the Central Filament of the Serpens South Protocluster

### 2014-12-17 Paper/paper.tex
modified:   Paper/paper.pdf 	modified:   Paper/paper.tex 	modified:   git_add.sh 	new file:   uv_space.png

We present 4.14 and 6.31 centimeter continuum observations of the Serpens South protocluster with the Karl G. Jansky Very Large Array in its C configuration. Our focus is a 4' x 4' area around the central filament ($\alpha=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta=-02^{\circ}02^{'}30.0^{''}$, J2000.0). We detect roughly 18 sources, 10 of which are probably protostellar in nature. We characterize the radio emission and put it in context with 2MASS, Spitzer and Herschel data from the region. We find new embedded protostars that have yet to be resolved at shorter wavelengths, and in some cases confirm compact centimeter emission in previously labeled starless cores. We compare our radio sources to the known centimeter vs. bolometric luminosity relationship. With our relatively short integration time and weak detection of many more possible radio sources, we speculate that longer, higher resolution radio measurements of the region would yield confident detections of many more radio protostars.

@@

	Serpens South is a young stellar cluster that is a part of the broader Aquila Rift extinction feature. It lies south of the Serpens Main cloud and is just West of the bright W40 HII region. Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars suggesting it is in a very early phase of cluster formation. Since its discovery, it has become the center of a wide range of scholarship. This has consisted of near, mid and far infrared mappings with Spitzer and Herschel tracing heated dust around protostars \citep{Gutermuth08, Bontemps10}, millimeter mappings with MAMBO on the IRAM 30-meter tracing cold dust \citep{Maury11}, near infrared polarimetry revealing the importance of global magnetic fields in the cluster's formation history \citep{Sugitani11}, molecular outflows studies \citep{Nakamura11, Teixeira12}, and a wealth of spectral line surveys probing filamentary infall \citep{Kirk13, Friesen13, Tanaka13, FernandezLopez14,Nakamura14a}. X-ray studies of Serpens South have yet to be published. Presently only one radio study of Serpens South has been conducted, which used the VLA in its A configuration in 2011 (Ortiz-Leon et al. in prep).

@@

	The VLA has been a proven tool in searching for and detecting radio emission around protostars since the early 1990s \citep[e.g.,][]{Curiel89, Anglada98, Reipurth99, Beltran01, Eiroa05, Shirley07, Rodriguez10}. Early radio studies of protostars found an excess of radio emission in comparison to the Lyman-Alpha continuum drop off expected from a normal ZAMS star. Theory and observations have best explained protostellar radio emission as having two components, thermal and non-thermal. Thermal radio emission is generally assumed to be free-free emission created from an HII region. High mass protostars have a high enough internal luminosity to support a compact or ultra-compact HII region, however, low mass protostars do not. HII regions surrounding low-mass protostars are created from thermal jets that shock the material surrounding the protostar. Non-thermal emission around low and high mass protostars is still not clearly understood; it is thought to come from gyrosynchrotron emission or possibly from jets that produce synchrotron emission in their tails.

@@

%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
\capstartfalse
\begin{deluxetable}{cccc}
\tabletypesize{\footnotesize}
\tablecaption{EVLA Image Properties}
\tablehead{
	\multicolumn{1}{c}{Wavelength}			&
	\multicolumn{1}{c}{Beam Size$^{a}$}		&
	\multicolumn{1}{c}{Position Angle}			&
	\multicolumn{1}{c}{Image RMS}					\\
	\colhead{(cm)}							&
	\colhead{(arcsec x arcsec)}					&
	\colhead{(degrees)}							&
	\colhead{($\mu$Jy beam$^{-1}$)}			}
\startdata
6.31	&	4.8 x 3.9	&	13.4	&	11.1	\\[1ex]
4.14	&	3.2 x 2.5	&	12.7	&	8.5
\enddata
\tablenotetext{a}{Deconvolved with robust weighting, \emph{robust}=0.5 \citep{Briggs95}.}
\label{tab:image_pars}
\end{deluxetable}
\capstarttrue
%%%%%%%%%%% End Table %%%%%%%%%%%%%%%

We observed Serpens South on July 2, 2013, for 1 hour with the EVLA in its C array configuration. The increased bandwidth of the EVLA allowed us to split our C band observation into two subbands centered at 4.75 GHz (6.31 cm) and 7.25 GHz (4.14 cm), with a bandwidth of 1.024 GHz for each subband. We focused on a 3.5 arcsec x 3.5 arcsec region around Serpens South's central filament, with a phase center positioned at $\alpha(\text{J2000})=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta(\text{J2000})=-02^{\circ}02^{'}30.0^{''}$. Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour-long observation. \autoref{fig:serpsouth_fov} shows Serpens South at 350 micron and outlines our field of view.

@@

We manually flagged, calibrated and imaged our data with standard procedures using Common Astronomy Software Applications (CASA) 4.1.0. We used J1331+305 (3C286) as a flux and bandpass calibrator, and J1804+0101 as a gain and phase calibrator ($S_{6.31\text{cm}}$ = 0.70 $\pm$ 0.02 Jy, $S_{4.14\text{cm}}$ = 0.66 $\pm$ 0.02 Jy). We deconvolved the Stokes $I$ images with the Cotton-Schwab algorithm \citep{Schwab84} using the CLEAN method \citep{Hogbom74,Clark80}. We experimented with natural, robust and uniform weighting, and found the best compromise between noise level and source resolution with robust weighting, also known as Briggs weighting \citep{Briggs95}, with a \emph{robust} parameter set to 0.5. The synthesized beam sizes and RMS values for our two images are detailed in \autoref{tab:image_pars}. We also deconvolved the Stokes $V$ images, but did not find any significant signal.

>>>>

We present 4.14 and 6.31 centimeter continuum observations of the Serpens South protocluster with the Karl G. Jansky Very Large Array in its C configuration. Our focus is a 3.5' x 3.5' area around the central filament. We detect roughly 18 sources, 10 of which are probably protostellar in nature. We characterize the radio emission and put it in context with 2MASS, Spitzer and Herschel data from the region. We find new embedded protostars that have yet to be resolved at shorter wavelengths, and in some cases confirm compact centimeter emission in previously identified starless cores. We compare our radio sources to the known centimeter vs. bolometric luminosity relationship. With our relatively short integration time and weak detection of many more possible radio sources, we speculate that longer, higher resolution radio measurements of the region would yield confident detections of many more protostars at centimeter wavelengths.

@@

	Serpens South is a young stellar cluster that is a part of the broader Aquila Rift extinction feature. It lies south of the Serpens Main cloud and is just West of the bright W40 HII region. Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars suggesting it is in a very early phase of cluster formation. Since its discovery, it has become the center of a wide range of scholarship. This has consisted of near, mid and far infrared mappings with Spitzer and Herschel tracing heated dust around protostars \citep{Gutermuth08, Bontemps10}, millimeter mappings with MAMBO on the IRAM 30-meter tracing cold dust \citep{Maury11}, near infrared polarimetry revealing the importance of global magnetic fields in the cluster's formation history \citep{Sugitani11}, molecular outflows studies \citep{Nakamura11, Teixeira12}, and a wealth of spectral line surveys probing filamentary infall \citep{Kirk13, Friesen13, Tanaka13, FernandezLopez14,Nakamura14a}. X-ray studies of Serpens South have yet to be published. Presently only one radio study of Serpens South has been conducted, which used the Karl G. Jansky Very Large Array (VLA) in its A configuration in 2011 (Ortiz-Leon et al. in prep).

@@

	The VLA has been a proven tool in searching for and detecting radio emission around protostars since the early 1990s \citep[e.g.,][]{Curiel89, Anglada98, Reipurth99, Beltran01, Eiroa05, Shirley07, Rodriguez10}. Early radio studies of protostars found an excess of radio emission in comparison to the Lyman-Alpha continuum drop off expected from a normal ZAMS star. Theory and observations have best explained protostellar radio emission as having two components, thermal and non-thermal. Thermal radio emission is generally assumed to be free-free emission created from an HII region. High mass protostars have a high enough internal luminosity to support a compact or ultra-compact HII region, however, low mass protostars do not. Free-free emission around low-mass protostars arises from shocks at the base of protostellar jets that shock the surrounding envelope material. Non-thermal emission around young (Class 0 and I), low and high mass protostars is still not clearly understood; it is thought to come from gyrosynchrotron emission created by stellar magnetic fields. (The gyrosynchrotron can also be magnetic reconnection events in their coronae I believe, check some of the recent Goulds Belt distance papers for their explanations.) %or possibly from jets that produce synchrotron emission in their tails.

@@

%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
\capstartfalse
\begin{deluxetable}{cccc}
\tabletypesize{\footnotesize}
\tablecaption{VLA Image Properties}
\tablehead{
	\multicolumn{1}{c}{Wavelength}			&
	\multicolumn{1}{c}{Beam Size$^{a}$}		&
	\multicolumn{1}{c}{Position Angle}			&
	\multicolumn{1}{c}{Image RMS}					\\
	\colhead{(cm)}							&
	\colhead{(arcsec x arcsec)}					&
	\colhead{(degrees)}							&
	\colhead{($\mu$Jy beam$^{-1}$)}			}
\startdata
6.31	&	4.8 x 3.9	&	13.4	&	11.1	\\[1ex]
4.14	&	3.2 x 2.5	&	12.7	&	8.5
\enddata
\tablenotetext{a}{Deconvolved with robust weighting, \emph{robust}=0.5 \citep{Briggs95}.}
\label{tab:image_pars}
\end{deluxetable}
\capstarttrue
%%%%%%%%%%% End Table %%%%%%%%%%%%%%%

We observed Serpens South on July 2, 2013, for 1 hour with the EVLA in its C array configuration. The increased bandwidth of the EVLA allowed us to split our C band observation into two subbands centered at 4.75 GHz (6.31 cm) and 7.25 GHz (4.14 cm), with a bandwidth of 1.024 GHz for each subband. We focused on a 3.5 arcmin x 3.5 arcmin region around Serpens South's central filament, with a phase center positioned at $\alpha(\text{J2000})=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta(\text{J2000})=-02^{\circ}02^{'}30.0^{''}$. The 6.31 and 4.14 cm images had primary beam diameters of 9.5 and 6.2 arcminutes respectively. Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour-long observation. \autoref{fig:serpsouth_fov} shows Serpens South at 350 micron and outlines our field of view.

@@

We manually flagged, calibrated and imaged our data with standard procedures using Common Astronomy Software Applications (CASA) 4.1.0. We used J1331+305 (3C286) as a flux and bandpass calibrator, and J1804+0101 as a gain and phase calibrator ($S_{6.31\text{cm}}$ = 0.70 $\pm$ 0.02 Jy, $S_{4.14\text{cm}}$ = 0.66 $\pm$ 0.02 Jy). We deconvolved the Stokes $I$ images with the Cotton-Schwab algorithm \citep{Schwab84} using the CLEAN method \citep{Hogbom74,Clark80}. We experimented with natural, robust and uniform weighting, and found the best compromise between noise level and source resolution with robust weighting, also known as Briggs weighting \citep{Briggs95}, with a \emph{robust} parameter set to 0.5. The synthesized beam sizes and RMS values for our two images are detailed in \autoref{tab:image_pars}.
